00_datawrangling.Rmd

### 2019-04-09 analysis/00_datawrangling.Rmd
improve manipulation factors

# relabel incorrectly named variables 
unique(colData$treatmentTemp)
colData$treatment <- ifelse(grepl("extend-hatch", colData$treatmentTemp), "extend", colData$treatmentTemp)

# drop no-longer-needed cols
colData <- colData %>% dplyr::select(-c(temp, treatmentTemp))

>>>>

# relabel incorrectly named variables 
colData$treatment <- ifelse(grepl("extend-hatch", colData$treatmentTemp), "extend",
                            ifelse(grepl("inc-prolong", colData$treatmentTemp), "prolong",
                                   ifelse(grepl("m.hatch", colData$treatmentTemp), "m.n2",
                                   colData$treatmentTemp)))

# drop no-longer-needed cols
colData <- colData %>% dplyr::select(-c(temp, treatmentTemp, NYNO))
